\section*{Bibliografía}
\addcontentsline{toc}{section}{Bibliografía}

\begin{thebibliography}{99}
	\bibitem{Beck2001}
	Beck, K., Beedle, M., Van Bennekum, A., Cockburn, A., Cunningham, W., Fowler, M., Grenning, J., Highsmith, J., Horn, J., Kan, D., Kern, J., Martin, R., McBride, B., Schwaber, K., Sutherland, J., Thomas, D., \& Wirfs-Brock, R. (2001).
	\textit{Manifesto for Agile Software Development.} (1st ed., p. 1).
	\url{https://agilemanifesto.org/iso/es/principles.html}
	\bibitem{Cohn2004}
	Cohn, M. (2004).
	\textit{User Stories Applied for Agile Software Development} (1st ed., p. 4).
	Addison-Wesley.
	\url{https://athena.ecs.csus.edu/~buckley/CSc191/User-Stories-Applied-Mike-Cohn.pdf}
	\bibitem{Cohn2005}
	Cohn, M. (2005).
	\textit{Agile Estimating and Planning} (1st ed., p. 52).
	PEARSON INDIA.
	\url{https://www.stat.cmu.edu/~brian/nynke/726-2021/612%20materials/36-612_Agile%20Estimating%20and%20Planning%20by%20Mike%20Cohn.pdf}
	\bibitem{DSDM2014}
	Dynamic Systems Development Method Consortium. (2014).
	\textit{The DSDM Agile Project Framework Handbook.} (c. 10).
	DSDM Consortium.
	\url{https://www.agilebusiness.org/dsdm-project-framework/moscow-prioririsation.html}
	\bibitem{Grance2011}
	Grance, T., \& Mell, P. (2011).
	\textit{The NIST Definition of Cloud Computing} (Special Publication 800-145, p. 2).
	National Institute of Standards and Technology.
	\url{https://nvlpubs.nist.gov/nistpubs/Legacy/SP/nistspecialpublication800-145.pdf}
	\bibitem{IEEE830-1998}
	IEEE Computer Society. (1998).
	\textit{IEEE Standard for Software Requirements Specifications} (IEEE Std 830-1998, p. 4).
	IEEE Computer Society.
	\url{http://www.math.uaa.alaska.edu/~afkjm/cs401/IEEE830.pdf}
	\bibitem{Karlsson1997}
	Karlsson, A., \& Ryan, C. (1997).
	\textit{A Cost–Value Approach for Prioritizing Requirements} (2nd ed., p. 68).
	IEEE SOFTWARE.
	\url{https://fileadmin.cs.lth.se/cs/Education/ETSF30/Labb/karlsson97.pdf}
	\bibitem{Morris2016}
	Morris, K. (2016).
	\textit{Infrastructure as Code: Managing Servers in the Cloud} (1st ed., p. 11).
	O'Reilly.
	\url{https://cdn.studio.f5.com/files/k6fem79d/production/1d0347b9629ac31ad62121114f0667508101f693.pdf}
	\bibitem{PMI2021}
	Project Management Institute. (2021)
	\textit{A Guide to the Project Management Body of Knowledge (PMBOK Guide)} (7th ed., p. 83).
	PMI Publications.
	\url{https://ibimone.com/PMBOK%207th%20Edition%20(iBIMOne.com).pdf}
	\bibitem{Schwaber2020}
	Schwaber, K., \& Sutherland, J. (2020).
	\textit{The Scrum Guide. The Definitive Guide to Scrum: The Rules of the Game.} (2020 ed., p. 7).
	Scrum.org.
	\url{https://scrumguides.org/docs/scrumguide/v2020/2020-Scrum-Guide-US.pdf}
	\bibitem{Sommerville2010}
	Sommerville, I. (2010).
	\textit{Software Engineering} (9th ed., p. 83).
	Addison-Wesley.
	\url{https://engineering.futureuniversity.com/BOOKS%20FOR%20IT/Software-Engineering-9th-Edition-by-Ian-Sommerville.pdf}
	\bibitem{Wiegers2013}
	Wiegers, K. E., \& Beatty, J. (2013).
	\textit{Software Requirements} (3rd ed., p. 10).
	Microsoft Press.
	\url{https://olivroqueaprende.com/WDK/Software_Requirements_3rd_Edition.pdf}
\end{thebibliography}